# the following exercises are a test in disguise. 
# what do you think about the coding? 
# can you think of any improvements to the following?

# install.packages("tidyverse") #uncomment to install tidyverse if you haven't already


```{r}
library(tidyverse)
```

## PROBLEM 1 ##

> visualizing your data is important!
> summary statistics can be highly misleading, and simply plotting the data can reveal a lot more!
> Lets look at the Anscombe’s Quartet data. There are four different data sets.
> Anscombe, F. J. (1973). "Graphs in Statistical Analysis". American Statistician. 27 (1): 17–21. doi:10.1080/00031305.1973.10478966. JSTOR 2682899.


```{r}
anscombe_quartet = readRDS("../dataset/anscombe_quartet.rds")
```

# let's explore the dataset 
```{r}
str(anscombe_quartet)
```


# what does the function str() do? 


# let's check some summary statistics:

```{r}
anscombe_quartet %>% 
  group_by(dataset) %>% 
  summarise(
    mean_x    = mean(x),
    mean_y    = mean(y),
    min_x     = min(x),
    min_y     = min(y),
    max_x     = max(x),
    max_y     = max(y),
    crrltn    = cor(x, y)
  )
```


# what do the summary statistics tell us about the different datasets? 

# let's plot the data with ggplot:

```{r}
require(ggplot2)

 ggplot(anscombe_quartet, aes(x=x,y=y)) +
  geom_point() + 
  geom_smooth(method = "lm",formula = "y ~ x") +
  facet_wrap(~dataset)
```


#save the plot

```{r}
ggsave("anscombe_quartet.png", width = 20, height = 20, units = "cm")
```


# what do the plots tell us about the different datasets? 
# describe the relationship between x and y in the different datasets. 

# would linear regression be an appropriate statistical model to analyse the x-y relationship in each dataset?
no
# what conclusions can you draw for the plots and summary statistics? 




## PROBLEM 2 ##

# load in the datasaurus dataset
```{r}
datasaurus_dozen = readRDS("../dataset/datasaurus_dozen.rds")
```


# explore the dataset 
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  count()

datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarise(
    mean_x    = mean(x),
    mean_y    = mean(y),
    min_x     = min(x),
    min_y     = min(y),
    max_x     = max(x),
    max_y     = max(y)
  )
```

# how many rows and columns does the datasaurus_dozen file have? 
1846 3 
# plot the dataset 
```{r}
ggplot(datasaurus_dozen, aes(x=x,y=y)) +
  geom_point() + 
  facet_wrap(~dataset)
```

# calculate the correlations and summary statistics for x and y in all datasets: 
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarise(
    crrltn = cor(x, y))
```

# Plot the relationships between x and y in each dataset including the line of best fit.
```{r}
ggplot(datasaurus_dozen, aes(x=x,y=y)) +
  geom_point() + 
  geom_smooth(method = "lm",formula = "y ~ x") +
  facet_wrap(~dataset)
```

# save the plot 
```{r}
ggsave("datasaurus_dozen.png", width = 20, height = 20, units = "cm")

```

# what conclusions can you draw for the plots and summary statistics? 
lm may not be the best model to use for these datasets